The Young Planet DS Tuc Ab has a Low Obliquity

### 2019-10-22 paper/main.tex
paper only missing one subsection

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\kep}{{\it Kepler}}
\newcommand{\kt}{{\it K2}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\ffis}{Full-Frame Images}
\newcommand{\fulltess}{{\it Transiting Exoplanet Survey Satellite}}
\newcommand{\Gaia}{{\it Gaia}}
\newcommand{\spitz}{{\it Spitzer}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\teff}{$T_{ eff}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

%\correspondingauthor{Benjamin~T.~Montet; \twitter{benmontet}}
\email{b.montet@unsw.edu.au}

@@

The abundance of short-period planetary systems with high obliquities is often taken as evidence that scattering processes play important roles in the formation and evolution of these systems.
More recent studies have suggested that wide binary companions can tilt protoplanetary disks, inducing a high obliquity on planets that form through smooth processes like disk migration.
\object{DS Tuc Ab}, a planet in the 45 Myr Tucana-Horologium association, likely traces its now-dissipated protoplanetary disk, enabling us to test these theories of disk physics. 
Here, we report on Rossiter-McLaughlin observations of one transit of DS Tuc Ab with the Planet Finder Spectrograph on the Magellan Clay Telescope at Las Campanas Observatory. 
We confirm the previously statistically validated planet by modeling the planet transit and stellar activity signals simultaneously, finding its obliquity to be low: $\psi = 12 \pm 13$ degrees. 
This is the youngest planet to be observed using this technique; we provide a discussion on best practices to accurately measure the observed signal of similar young planets.
\end{abstract}

@@

Planets in young clusters are valuable resources to provide clean test cases for planet formation. 
Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out certain dynamical interactions, meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk.

Therefore, by measuring the obliquity of the orbits of young planets relative to the spin of their host stars, we are tracing the obliquity of their disks. 
Observing a population of these systems will allow us to understand statistical disk properties. 
Alignment of planetary systems and their host stars is often taken as evidence in favor of smooth migration processes. \btmtodo{cite papers here}. 
However, \btmtodo{Batygin citation} suggest wide binary companions or nearby stars in the birth cluster can torque disks to random inclinations over the lifetime of the disk. With a statistical sample of the obliquities of young planets, we can test this hypothesis.

Such a survey is limited by the small number of planetary systems around young stars. There are only a handful of planets known to be younger than 100 Myr, identified by their membership in young moving groups or star forming regions \btmtodo{citep David19, Mann, others}.

Recently, data from the Transiting Exoplanet Survey Satellite \citep{Ricker14} were used to identify a planet with an orbital period of 8.14 days around the star \object{DS Tuc A} \citep{Benatti19, Newton19}. 
DS Tuc is a member of the Tucana-Horologium (Tuc-Hor) assocation, which has an age of approximately 45 Myr \btmtodo{cite!}. 
DS Tuc itself is a binary with a projected separation of \btmtodo{AU}. 
From \citet{Holman97}, the timescale for Kozai-Lidov interactions is
\begin{equation}
    \tau \approx P_\textrm{planet} \frac{M_\star}{M_\textrm{pert}} \bigg(\frac{a_\textrm{pert}}{a_\textrm{planet}}\bigg)^3 (1-e^2_\textrm{pert})^{3/2},
\label{eq:timescale}
\end{equation}
where $P_\textrm{planet}$ is the the orbital period of a planet with orbital semimajor axis  $a_\textrm{planet}$ about a host of mass $M_\star$, $M_\textrm{pert}$ is the
mass of the perturbing star, and $a_\textrm{pert}$ and $e_\textrm{pert}$ the semimajor axis and eccentricity of the outer object's orbit around the host star/planet system.

From the orbital parameters in \citet{Newton19}, ${M_\star}/{M_\textrm{pert}} \approx 1.2$, ${a_\textrm{pert}}/{a_\textrm{planet}} \approx 2000$, and $(1-e^2_\textrm{pert})^{3/2} \approx 0.5$, so the timescale $\tau$ from Equation \ref{eq:timescale} is more than 100 Myr.

Therefore, this planet likely traces the orientation of the now-dissipated protoplanetary disk. 
Measuring the obliquity of the planet relative to the star thus enables us to test theories of disk torqing.
We can measure the obliquity between the spin of the star and the orbit of the planet through the Rossiter-McLaughlin effect, in which an apparent redshift and blueshift in the radial velocity of the star are observed as a transiting planet occults the blueshifted and redshifted hemispheres of the rotating star, respectively \citep{Rossiter24, McLaughlin24}.
DS Tuc Ab is the youngest known planet for which such an observation has been attempted, providing us the nearest test case to an undissipated disk yet acheivable.

@@

We obtained data with the Planet Finder Spectrograph (PFS) on the Magellan Clay Telescope \citep{Crane06, Crane08, Crane10}. 
On \btmtodo{date} from \btmtodo{time} to \btmtodo{time} we obtained \btmtodo{number} of measurements of the RV of DS Tuc A. The transit duration is 190 minutes, meaning approximately 50\% of the data were obtained in transit while the other half provide information about the out-of-transit RV baseline. Each exposure was 360 seconds in length and was taken with the \btmtodo{slit} slit, which provides a resolution $R \approx$ \btmtodo{number} per btmtodo{pixel or resolution element?}. All observations were taken with the iodine cell in place \citep{Marcy92}, which imprints a series of narrow lines at known wavelengths to measure the instrument point spread function and wavelength solution at each epoch.

@@

To characterize the stellar activity-induced variations, we also obtained \btmtodo{more}
These observations had exposure lengths varying from 360 to 600 seconds under variable sky conditions, with the goal of achieving a similar SNR in each of these spectra as during the night of the transit.

We also collected a template spectrum of DS Tuc A immediately after the transit observations. 
This spectrum, obtained under similar conditions and with the same slit but without the iodine cell in the light path, is used in the pipeline RV modeling.
All observations were then analyzed using the standard PFS pipeline \citep{Butler96}, which divides the spectrum into 2\AA\ chunks and fits each chunk independently.
The resultant RV is the weighted mean of the RVs of each chunk, and the provided uncertainty is the standard deviation of these velocities.

\btmtodo{Paragraph here about what RVs are included in the modeling}

@@

\input{datatable.tex}

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.5\textwidth, trim={0cm 0.0cm 0cm 0cm}, clip=true]{../figures/all_data.pdf}
   \end{center}
  \caption{RV time series for (left) the observed transit and (right) a timespan covering approximately one stellar rotation period. Note the different vertical scalings on each subplot. The Rossiter-McLaughlin signal is easily detectable, occurring over a significantly different timescale than the rotationally-induced variability signal.}
  \label{fig:data}
\end{figure}

@@

\btmtodo{Mention that we force circular orbits}

\subsection{Model}

Over the six hours of the transit, the apparent radial velocity of the star increases by \btmtodo{number} m s$^{-1}$. 
In Section \ref{sec:trend} we argue this trend is due to stellar activity rather than an additional planet.
To understand the obliquity of the transiting planet, for now we are only concerned with appropriately modeling this signal.
We attempt to model this signal through multiple approaches.
We use low-order polynomials, up to the third degree, to fit the extra variability during the night of the transit. 
We also build a stellar activity model by fitting a function that is a linear sum of the observed $H\alpha$ and calcium $S_{HK}$ measurements during the night, which are correlated with the observed RV.
Finally, we also fit \textit{starry} models of a single starspot in time. The spot is modeled as a Gaussian darker region on the surface of the star; we allow the spot's size, contrast, and location to vary as we fit both signals.

In each case, we then build a model that is the sum of the R-M signal and the stellar activity signal at each cadence, such that
With three separate models, we can use the inferred likelihood to compare the abilities of these activity models to fit the data. 
It also gives us the opportunity to verify that the resultant obliquity measurement does not depend on the specific prescription of the stellar activity signal.

\btmtodo{this whole section uses the term `model' too much}

@@

To compare the data to our model, we need to write down a likelihood function. 
Each observation has an associated uncertainty, calculated as the \todo{pfs team}{red}{how exactly are the uncertainties calculated in the PFS pipeline?}
For this young and active star, this likelihood may not represent the true uncertainty in the measured RV at each epoch. 
For example, occultations of small spots across the surface of the star could cause the observed RV to vary from epoch to epoch. 
Additionally, stellar flares would have characteristic timescales similar to a single exposure and could impact the observed RV if a significant amount of emission from the star was ejected from the surface of the star with considerable velocity \btmtodo{cite here}.

We test multiple likelihood functions with the same form.
First, we assume a model that is the sum of two Gaussians with the same mean but different variance. 
Under this model, each data point has some probability $q$ of being a ``good'' data point drawn from a relatively narrow distribution. This distribution is a combination of the PFS pipeline uncertainty and an additional jitter term, added in quadrature. 
Each data point also has a probability $1-q$ of being drawn from a much broader distribution. We allow the width of both Gaussian distributions to vary in our fitting procedure. 
Additionally, $q$ is a free parameter: if the data were well-modeled by a single Gaussian, we would find the posterior distribution on $q$ to be consistent with zero.

These two Gaussians do not need to have the same mean. 
The surface of the star, as a rapidly rotating G dwarf, is likely dominated by dark starspots rather than bright faculae \citep{Montet17}. 
Each dark spot will have the effect of inducing a signal with roughly the same shape as the R-M effect for an aligned system: as the spot occults the blueshifted hemisphere of the star, it will induce an apparent redshift and vice versa.
As a planet occults a spot then, just as this phenomenon produces a brief brightening in a transit light curve \btmtodo{cite spot crossing papers here} a spot-crossing event would cause a temporary decrease in the magnitude of the Rossiter-McLaughlin signal. 
We then allow for the broader Gaussian in our mixture model to be offset by some factor which is directly proportional to the magnitude of the R-M signal at that epoch. The mean of our second Gaussian is then
\begin{equation}
\mu_2 = \alpha (RV_{RM}).
\end{equation}
When $\alpha = 1$, the means of the two Gaussians overlap precisely, leaving us with a standard mixture model as might be expected if the extra variability was not related to starspots. 
We test both the case where $\alpha$ is set equal to 1, and also allowed to vary as a free parameter.

Our full likelihood function is then
\begin{equation}
\mathcal{L} \propto 1	
\end{equation}
\btmtodo{write this out}
where \btmtodo{stuff equals stuff}

@@

Don't forget to mention our priors here!

Something in the models subsubsection about Halpha being less noisy than Shk for this star. Probably because of the wavelengths we're dealing with?

Gee, MCMC sure is cool.

@@

$10 \pm 10$ degrees, roughly.

\begin{deluxetable*}{lccc}[!ht]
\tablecaption{Inferred transit parameters \label{tab:results}}
\tablehead{
\colhead{} & \colhead{Polynomial Model} & \colhead{Stellar Activity Correlation Model} & \colhead{Starspot Fit} 
}
\startdata
\vsini\ (km s$^{-1}$) & $19.6 \pm 1.5$ & $20.0 \pm 1.6$ & $19.4 \pm 1.5$ \\
$R_p/R_\star$ & $0.059 \pm 0.002$ & $0.060 \pm 0.003$ & $0.059 \pm 0.002$ \\
$t_0$ ($\textrm{BJD}-2457000$) & $1706.6654 \pm 0.0010$ & $1706.6653 \pm 0.0018$ &
              $1706.6655 \pm 0.0012$\\
$b$ & $0.18 \pm 0.11$ & $0.17 \pm 0.13$ & $0.18 \pm 0.12$ \\
$a/$\rstar & $20.8 \pm 0.7$ & $21.2 \pm 1.1$ & $20.9 \pm 0.8$ \\
Obliquity (deg) & $14 \pm 11$ & $5 \pm 11$ & $12 \pm 13$ \\
Obliquity (deg), $q=1$ & $12 \pm 11$ & $13 \pm 6$ & $7 \pm 12$ \\
Obliquity (deg), $\alpha = 1$ & $14 \pm 13$ & $3 \pm 11$ & $8 \pm 15$ \\
\hline
Spot Amplitude & - & - & $0.019 \pm 0.005$ \\
Spot Size (\rstar) & - & - & $0.055 \pm 0.023$ \\
Spot Longitude\tablenotemark{a} (deg) & - & - & $26 \pm 4$ \\
Spot Latitude\tablenotemark{a} (deg) & - & - & $28 \pm 8$ \\
\hline
jitter 1 (m s$^{-1}$) & $1.8 \pm 0.9$ & $1.5 \pm 0.9$ & $1.8 \pm 0.9$ \\
jitter 2 (m s$^{-1}$) & $8.8 \pm 4.4$ & $11.9 \pm 3.0$ & $9.3 \pm 5.4$ \\
$q$ & $0.54 \pm 0.24$ & $0.32 \pm 0.17$ & $0.58 \pm 0.24$ \\
$\alpha$ & $0.88 \pm 0.08$ & $0.88 \pm 0.11$ & $0.85 \pm 0.15$ \\
\hline
$\log \mathcal{L}_\textrm{max}$ & $-162.2$ & $-178.3$ & $-162.1$ \\
Bayes' Factor & 0.83 & $9.1 \times 10^{-8} $ & 1.0
\enddata
\tablenotetext{a}{Defined at $\textrm{BJD}-2457000 = 1706.5$}
\end{deluxetable*}

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.45\textwidth, trim={0cm 0.0cm 1cm 1cm}, clip=true]{../figures/model_comp1.pdf}
   \end{center}
  \caption{Draws from the posterior distributions of a simultaneous fit to the
  Rossiter-McLaughlin signal and three different noise models. Green curves represent the noise model, while orange curves include the transit signal as well. From top to bottom, the noise models are a simple cubic polynomial fit, a fit regressed against the spectral stellar activity indicators, and a starspot model built with the \textit{starry} package of \citep{Luger19}. The polynomial and starspot models provide similar quality fits to the data, both of which find significantly higher log likelihood values than the third fit. Significantly, all give consistent results on the measured spin-orbit obliquity angle of approximately $12 \pm 12$ degrees.}
  \label{fig:models}
\end{figure}

@@

Mention the fast rotation of the star, vsini of like 17 km/s? And the measured rotation period here. Wouldn't hurt to include the eleanor light curve so people can see the rotation and the magnitude of the spots, and it gets us an easy citation.

@@

\subsection{Long-term trend}

Over the six hours of the transit, the apparent RV of the star increases at approximately 10 m s$^{-1}$ hr$^{-1}$. 
In Section \ref{sec:analysis}, we model this RV shift using a toy model of a single 
starspot group moving across the surface of the star, finding this provides an appropriate fit to the data. 
However, we also use low-order polynomials to attempt to fit the data, finding that simple hueristic works approximately equally well.
This could, in principle, be caused by observing a fraction of a Keplerian orbit from another object orbiting inducing an RV shift on the star. 
We can easily rule out the wide binary companion as the culprit.
From \citet{Liu02}, the RV acceleration from a wide binary companion with mass $m$ at a known separation $\rho$ observed at a distance $d$ is always bounded such that:
\begin{equation}
    \frac{d\textrm{RV}}{dt} < 197 \textrm{m } \textrm{s}^{-1} \textrm{ d}^{-1}
    \frac{m}{M_\odot} \bigg(\frac{d}{1\textrm{pc}}\bigg)^{-2} \bigg(\frac{\rho}{1''}\bigg)^{2}.
\end{equation}
For this companion, the RV trend induced must be no more than 1 m s$^{-1}$ yr$^{-1}$, much less than the observed acceleration.

@@

Such a companion need only be stable for a relatively short time given the age of the system; a companion similar to this one would likely induce significant TTVs which could be detected by continued transit monitoring.
However, starspot-induced modulation is a likely culprit which can explain the observed variability.

@@

This may explain the excess variability observed in the second half of our transit. 
Over this part of the transit, the observed point-to-point variability is larger, which may be the result of the planet crossing the relatively more inhomogenous hemisphere, causing an increase in the variability of the observed RV shift.

>>>>

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\kep}{{\it Kepler}}
\newcommand{\kt}{{\it K2}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\ffis}{Full-Frame Images}
\newcommand{\fulltess}{{\it Transiting Exoplanet Survey Satellite}}
\newcommand{\Gaia}{{\it Gaia}}
\newcommand{\spitz}{{\it Spitzer}}
\newcommand{\vsini}{{$v \sin i$}}
\newcommand{\teff}{$T_{ eff}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

\correspondingauthor{Benjamin~T.~Montet; \twitter{benmontet}}
\email{b.montet@unsw.edu.au}

@@

The abundance of short-period planetary systems with high obliquities is often taken as evidence that scattering processes play important roles in the formation and evolution of these systems.
More recent studies have suggested that wide binary companions can tilt protoplanetary disks, inducing a high obliquity on planets that form through smooth processes like disk migration.
\object{DS Tuc Ab}, a planet in the 40 Myr Tucana-Horologium association, likely traces its now-dissipated protoplanetary disk, enabling us to test these theories of disk physics. 
Here, we report on Rossiter-McLaughlin observations of one transit of DS Tuc Ab with the Planet Finder Spectrograph on the Magellan Clay Telescope at Las Campanas Observatory. 
We confirm the previously statistically validated planet by modeling the planet transit and stellar activity signals simultaneously, finding its obliquity to be low: $\psi = 12 \pm 13$ degrees. 
This is the youngest planet to be observed using this technique; we provide a discussion on best practices to accurately measure the observed signal of similar young planets.
\end{abstract}

@@

A population of low-obliquity planets is often considered a signature of smooth disk migration \citep{Morton11a, Ford14}. However, \citet{Albrecht12} show that obliquity is an imperfect tracer of the formation history for many stars, as the tidal realignment timescale for a massive, nearby planet can be shorter than the age of the system for many stars with convective outer layers.
\citet{Batygin12} suggest wide binary companions or nearby stars in the birth cluster can torque disks to random inclinations over the lifetime of the disk.

Planets in young clusters are valuable resources to provide clean test cases for planet formation. 
Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out many slow-timescales dynamical interactions meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk. 
With a statistical sample of the obliquities of young planets, we can test the hypothesis of \citet{Batygin12} to see if the torquing of a disk by a distant perturber is a common process.

Such a survey is limited by the small number of planetary systems around young stars. There are only a handful of transiting planets known to be younger than 100 Myr, identified by the host star's membership in young moving groups or star forming regions \citep{David16, Mann16, David19}.

Recently, data from the Transiting Exoplanet Survey Satellite \citep{Ricker14} were used to identify a planet with an orbital period of 8.14 days around the star \object{DS Tuc A} \citep{Benatti19, Newton19}. 
DS Tuc is a member of the Tucana-Horologium (Tuc-Hor) assocation, which has an age of 35-45 Myr \citep{Bell15, Crundall19}. 
DS Tuc itself is a binary with a projected separation of 240 AU. 
From \citet{Holman97}, the timescale for Kozai-Lidov interactions is
\begin{equation}
    \tau \approx P_\textrm{planet} \frac{M_\star}{M_\textrm{pert}} \bigg(\frac{a_\textrm{pert}}{a_\textrm{planet}}\bigg)^3 (1-e^2_\textrm{pert})^{3/2},
\label{eq:timescale}
\end{equation}
where $P_\textrm{planet}$ is the the orbital period of a planet with orbital semimajor axis  $a_\textrm{planet}$ about a host of mass $M_\star$, $M_\textrm{pert}$ is the
mass of the perturbing star, and $a_\textrm{pert}$ and $e_\textrm{pert}$ the semimajor axis and eccentricity of the outer object's orbit around the host star/planet system.

From the orbital parameters in \citet{Newton19}, ${M_\star}/{M_\textrm{pert}} \approx 1.2$, ${a_\textrm{pert}}/{a_\textrm{planet}} \approx 2000$, although the posterior distribution is highly skewed to larger values, and $(1-e^2_\textrm{pert})^{3/2} \approx 0.5$, so the timescale $\tau$ from Equation \ref{eq:timescale} is more than 100 Myr, and possibly much more depending on the true semimajor axis ratio.

As the age of the system is younger than this, even before considering the several million year timescale for planet formation, this planet likely traces the orientation of the now-dissipated protoplanetary disk. 
Measuring the obliquity of the planet relative to the star thus enables us to test theories of disk torqing.
We can measure the obliquity between the spin of the star and the orbit of the planet through the Rossiter-McLaughlin (R-M) effect, in which an apparent redshift and blueshift in the radial velocity of the star are observed as a transiting planet occults the blueshifted and redshifted hemispheres of the rotating star, respectively \citep{Rossiter24, McLaughlin24}.
DS Tuc Ab is the youngest known planet for which such an observation has been attempted, providing us the best laboratory we have to test this theory.
We note that Zhou et al. (in prep) also obtained two transits of this planet with PFS for a complimentary Doppler tomographic analysis of this system.

@@

We obtained data with the Planet Finder Spectrograph (PFS) on the Magellan Clay Telescope \citep{Crane06, Crane08, Crane10}. 
On 2019 Aug 11 from UT 01:12 to UT 07:10 we obtained 49 measurements of the RV of DS Tuc A. 
The transit duration is 190 minutes, meaning approximately 50\% of the data were obtained in transit while the other half provide information about the out-of-transit RV baseline. Each exposure was 360 seconds in length and was taken with the 0\farcs3 $\times$ 2\farcs5 slit, which provides a resolution $R \approx 80,000$ per resolution element. All observations were taken with the iodine cell in place \citep{Marcy92}, which imprints a series of narrow lines at known wavelengths to measure the instrument point spread function and wavelength solution at each epoch.

\todo{pfs team}{red}{Can you please add a couple sentences here describing how Shk and Halpha measurements are calculated? Is the proper unit Angstroms for the derived values, as presented in Table 1?}

To characterize the stellar activity-induca measurmeed variations, we also obtained twelve additional observations of DS Tuc A. These included four observations over two nights on 2019 Aug 21 and 2019 Aug 22, and eight observations over four nights from 2019 Sep 11 to 2019 Sep 14 (all dates UT).
These observations had exposure lengths varying from 360 to 600 seconds under variable sky conditions, with the goal of achieving a similar SNR in each of these spectra as during the night of the transit, and provide us the opportunity to measure the RV variability of the star on rotational period timescales.

We also collected a template spectrum of DS Tuc A on the night of the transit, immediately after the observations described above.
This spectrum, obtained under similar conditions and with the same slit but without the iodine cell in the light path, is used in the pipeline RV modeling.
All observations were then analyzed using the standard PFS pipeline \citep{Butler96}, which divides the spectrum into 2\AA\ chunks and fits each chunk independently.
The resultant RV is the weighted mean of the RVs of each chunk, and the provided uncertainty is the standard deviation of these velocities.

@@

In fitting the template to the data for the night of the transit, we tested a reduction using all available data and one only using data from the night of the transit, finding a lower point-to-point scatter with the latter strategy. 
This is likely due to changes in the line profile shape on rotational timescales as the stellar surface varies, which leads to a redefinition in the median behavior of each 2\AA\ chunk.
As additional points are added at different stellar activity levels, this median behavior becomes more and more discrepant from that observed on the night of the transit, leading to a noisier fit. 
As a result, we use two different reductions when considering the data from the night of the transit itself and from the later observations, which typically have approximately twice the RV uncertainity despite generally being observed to the same expected SNR.
This strategy means in practice, there may be an RV offset between the two sections of the data set, but as we only consider the data from the transit night itself when modeling the R-M signal, this should not affect our results.

@@

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.5\textwidth, trim={0cm 0.0cm 0cm 0cm}, clip=true]{../figures/all_data.pdf}
   \end{center}
  \caption{RV time series for (left) the observed transit and (right) a timespan covering approximately one stellar rotation period. Note the different vertical scalings on each subplot. The R-M signal is easily detectable, occurring over a significantly different timescale than the rotationally-induced variability signal.}
  \label{fig:data}
\end{figure}

@@

\subsection{Model}
\label{sec:model}

While the R-M signal model is always developed through \textit{starry} in our analysis, we test multiple approaches to model the effects of the star on these observations.
Over the six hours of the transit, the apparent radial velocity of the star increases by more than 50 s$^{-1}$. 
In Section \ref{sec:trend} we argue this trend is due to stellar activity rather than an additional unseen planet.
Regardless of the cause of this signal, in order to accurately measure the obliquity of the transiting planet we must model the underlying stellar behavior as well.
We test several different approaches to this problem to ensure our results are not sensitive to our assumptions about the star.
We use low-order polynomials, up to the third degree, to fit the relatively long-term variability during the night of the transit. 
We also build a stellar activity model by fitting a function that is a linear sum of the observed $H\alpha$ and calcium $S_{HK}$ measurements during the night, which are correlated with the observed RV.
Finally, we also fit \textit{starry} models of a single starspot in time. The spot is modeled as a Gaussian darker region on the surface of the star; we allow the spot's size, contrast, and location to vary as we fit both signals.

In each case, we can then calculate the expected sum of the R-M signal and the stellar activity signal at each cadence to compare to the data. 
This strategy allows us to understand in a relative sense how well each of the three models fit the data. 
It also gives us the opportunity to verify that the resultant obliquity measurement does not depend on the specific prescription of the stellar activity signal.

@@

To compare the data to our model, we need to write down a likelihood function. 
Each observation has an associated uncertainty, calculated as the weighted standard deviation of the calculated mean of each of the 2\AA\ chunks fit at each epoch.
For this young and active star, this likelihood may not represent the true uncertainty in the measured RV at each epoch. 
For example, occultations of small spots across the surface of the star could cause the observed RV to vary from epoch to epoch, similar to how starspots can affect the observed transit depth in photometric monitoring \citep{SanchisOjeda13}.
Additionally, stellar flares would have characteristic timescales similar to a single exposure have been shown to induce RV variations at the 10-100 m s$^{-1}$ level \citep{Reiners09}.

We test multiple likelihood functions with the same form.
First, we assume each data point is drawn from a mixture model which is the sum of two Gaussian functions, each with a different variance.
Under this model, each data point has some probability $q$ of being a ``good'' data point drawn from a relatively narrow distribution. This distribution is a combination of the PFS pipeline uncertainty and an additional jitter term, added in quadrature. 
Each data point also has a probability $1-q$ of being drawn from a much broader distribution, with a separate jitter term, to account for the possibility of stellar affects which significantly affect only a small number of data points. We allow the width of both Gaussian distributions to vary in our fitting procedure. 
Additionally, $q$ is a free parameter: if the data were well-modeled by a single Gaussian, we would find the posterior distribution on $q$ to be consistent with 1.0.
Forcing $q=1$ would have the same effect, fitting the data using only a single Gaussian.

These two Gaussians do not need to have the same mean. 
The surface of the star, as a rapidly rotating G dwarf, is likely dominated by dark starspots rather than bright faculae \citep{Montet17}. 
Each dark spot will induce a signal with roughly the same shape as the R-M effect for an aligned system: as the spot occults the blueshifted hemisphere of the star, it will induce an apparent redshift and vice versa.
As a planet occults a spot then, just as this phenomenon produces a brief brightening in a transit light curve \citep{Desert11, SanchisOjeda13, Morris17}, a spot-crossing event would cause a temporary decrease in the magnitude of the R-M signal. 
To allow for this effect in our fitting procedure, we allow for the broader Gaussian in our mixture model to be offset by some factor which is directly proportional to the magnitude of the R-M signal at that epoch.

When $\alpha = 1$, the means of the two Gaussians overlap precisely, leaving us with a standard mixture model as might be expected if the extra variability was not related to starspots. Again, $\alpha$ is fit as a free parameter, so if the data were well modeled as a mixture model of two Gaussians with the same mean, we would find the posterior on $\alpha$ would be consistent with 1.

Our full likelihood function is then
\begin{equation}
\begin{split}
\mathcal{L} = \prod_i \bigg[ & \frac{q}{\sqrt{2\pi (\sigma^2 + s_1^2)}} \exp\bigg(-\frac{(y_{p,i} + y_{s,i}-V_i)^2}{2(\sigma^2 + s_1^2)}\bigg)  \\+ & \frac{1-q}{\sqrt{2\pi s_2^2)}} \exp\bigg(-\frac{(\alpha y_{p,i} + y_{s,i}-V_i)^2}{2(s_2^2)}\bigg) \bigg],
\end{split}
\end{equation}
where $i$ iterates over all observations, $\sigma$ the instrument uncertainties, $s_1$ and $s_2$ the additional jitter terms, $V$ the measured RV values, $y_p$ the component of the measured velocity from the planetary R-M signal, and $y_s$ the stellar activity model signal. $\alpha$ and $q$ retain their definitions from the previous paragraphs in this section.

@@

As described in Section \ref{sec:model}, We test three different parameterizations to fit the long-term trend. 
We also test likelihood functions where $\alpha$ is fixed at 1.0 and models where $q$ is fixed at 1.0 (in which case $\alpha$ is undefined) for each parameterization, giving us nine total tests.

We fit these models to evaluate the posterior distribution using the \textit{emcee} package of \citet{Foreman-Mackey12}, an implementation of the affine-invariant ensemble sampler of \citet{Goodman10}.
For all explorations using the cubic polynomial out-of-transit model, we initialize 500 walkers; for all other runs we initialize 600 walkers. 
We run each for 3,000 steps, removing the first 2,000 as burn-in and considering the final 1,000 steps in our final analysis. 
We verify that our chains have converged following the method of \citet{Geweke92} and through visual inspection.

In our analysis, in calculating the orbit we assume exactly circular orbits. 
Given only information about the transit and assuming the orbital velocity of the planet does not change significantly during the transit there is a degeneracy between the eccentricity and the stellar size. 
We choose to force circular orbits and fit the orbital separation $a/$\rstar\ as a free parameter, although the opposite strategy would be equally valid.
We include uninformative priors on all parameters except for the projected rotational velocity \vsini\ and the radius ratio $R_p$/\rstar.
For both parameters, \citet{Benatti19} and \citet{Newton19} provide discrepant results; we conservatively apply Gaussian priors with means of 18.3 km s$^{-1}$ and 0.057 and standard deviations of 1.8 km s$^{-1}$ and 0.003 for \vsini\ and $R_p$/\rstar, respectively.

@@

Our results are given in Table \ref{tab:results}. 
The maximum likelihood of the stellar activity indicator model is significantly lower than that of the other models. 
The maximum likelihood $\log \mathcal{L}_\textrm{max}$ differs by only 0.1 between the \textit{starry} and polynomial models, but is substantially lower for the third model. 
This corresponds to a Bayes' factor of $\approx 10^{-7}$ when comparing this model to the \textit{starry} model.
In a statistical sense, our starspot model provides approximately an equally valid fit to the data as our simple polynomial model; both provide a much more plausible fit than the stellar activity indicator model.

All models provide broadly consistent results on the measured obliquity. Considering the two families of most plausible models, the median of the obliquity posterior varies from 7 to 14 degrees depending on the specific choice of model used.
All statistical uncertainties range from 11 to 15 degrees.
Using our general polynomial fit, allowing both $q$ and $\alpha$ to vary, we infer an obliquity of $14 \pm 11$ degrees.
Likewise, with our \textit{starry} model we infer an obliquity of $12 \pm 13$ degrees.
As this model provides the highest likelihood fit to the data we choose this set of values as most representative of our knowledge of the obliquity of the system, but we emphasize that the particular choice of model or likelihood function does not appear to significantly affect the inferred obliquity.

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.45\textwidth, trim={0cm 0.0cm 1cm 1cm}, clip=true]{../figures/model_comp1.pdf}
   \end{center}
  \caption{Draws from the posterior distributions of a simultaneous fit to the
  R-M signal and three different noise models. Green curves represent the noise model, while orange curves include the transit signal as well. From top to bottom, the noise models are a simple cubic polynomial fit, a fit regressed against the spectral stellar activity indicators, and a starspot model built with the \textit{starry} package of \citep{Luger19}. The polynomial and starspot models provide similar quality fits to the data, both of which find significantly higher log likelihood values than the third fit. Significantly, all give consistent results on the measured spin-orbit obliquity angle of approximately $12 \pm 12$ degrees. For visualization purposes, we interpolate the stellar activity indicator regression model between the observations with a cubic spline, although the fitting itself only requires this parameter to be defined at the times of the observations.}
  \label{fig:models}
\end{figure}

@@

@@

\subsection{Long-term trend}
\label{sec:trend}

Over the six hours of the transit, the apparent RV of the star increases at approximately 8 m s$^{-1}$ hr$^{-1}$. 
In Section \ref{sec:analysis}, we model this RV shift using a toy model of a single 
starspot group moving across the surface of the star, finding this provides an appropriate fit to the data. 
However, we also use low-order polynomials to attempt to fit the data, finding that simple hueristic works approximately equally well.
This could, in principle, be caused by observing a fraction of a Keplerian orbit from another object orbiting inducing an RV shift on the star. 
We can easily rule out the wide binary companion as the culprit.
From \citet{Liu02}, the RV acceleration from a wide binary companion with mass $m$ at a known separation $\rho$ observed at a distance $d$ is always bounded such that:
\begin{equation}
    \frac{d\textrm{RV}}{dt} < 197 \textrm{m } \textrm{s}^{-1} \textrm{ d}^{-1}
    \frac{m}{M_\odot} \bigg(\frac{d}{1\textrm{pc}}\bigg)^{-2} \bigg(\frac{\rho}{1''}\bigg)^{2}.
\end{equation}
For this companion, the RV trend induced must be no more than 1 m s$^{-1}$ yr$^{-1}$, much less than the observed acceleration.

@@

Such a companion need only be stable for a relatively short time given the age of the system; a companion similar to this one would likely induce significant TTVs which could be detected by continued transit monitoring.
Our additional obserations of the system, taken approximately 30 days after the transit and spread over four nights, do indeed show a signal consistent with a $\sim 3$ \mjup\ planet in a 2.8 day orbital period. However, this period is also consistent with the measured stellar rotation period from \tess\ photometry, suggesting this periodicity and the long-term behavior we observe during the night of the transit are more likely explained as starspot-induced modulation.

@@

This may explain the excess variability observed in the second half of our transit. 
Over this part of the transit, the observed point-to-point variability is larger, which may be the result of the planet crossing a relatively more inhomogenous hemisphere on observation timescales, causing an increase in the observed variability over this fraction of the observations.
